Analysis

### 2023-04-12 Analysis.rmd
update rank plot

ranks <- scores |>
  filter(model %in% models_non_human) |>
  summarise_scores() |>
  select(model, target_type, horizon, forecast_date, interval_score, scale, type_and_scale) |>
  group_by(target_type, scale, horizon, forecast_date) |>
  mutate(rank = rank(interval_score))

>>>>

```{r}
ranks <- scores |>
  filter(model %in% models_non_human) |>
  summarise_scores() |>
  select(model, target_type, horizon, forecast_date, interval_score, scale, type_and_scale) |>
  group_by(target_type, scale, horizon, forecast_date) |>
  mutate(rank = rank(interval_score))
